Assignment 4

### 2015-03-09 rmtw/a4/latex8.tex
adsffdsa

The next step was to perform outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.

\begin{figure}[Ht!]
\centering
\includegraphics[width=90mm]{uc_box.png}
\caption{Use Case Boxplot}
\end{figure}

\begin{figure}[Ht!]
\centering
\includegraphics[width=90mm]{cl_box.png}
\caption{Checklist Boxplot}
\end{figure}

Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test. The result of the WMW test was W=250, p=0.1063 and with the significance level of 89 (cite www.sussex) H0 is rejected. (Note that this was done on the raw data and not /45*60).

@@

1 and 2.
Box
->
Histo, QQ, kolmogorov, z-test?
->
T

3.
Z-test verkar vara ett alternativ till chi

* Method(s) for analyzing the data (Statistical analysis)

* Motivation of why these statistical tests where used

*Report the results

*Discuss what does the results means, how do we interpret it

@@

\verbatiminput{f_eff.txt}

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

\verbatiminput{t_eff.txt}

According to the test, the efficiency of CL is 7.3 while the efficiency of UC is 6.16 and H0 eff is therefore rejected.

\Section{Tests for rate}

\verbatiminput{f_rate.txt}

Since the p-value is larger than 0.05, we can deduce that the variances are homogeneous (cite expe) and that the T-test is the optimal approach.

\verbatiminput{t_rate.txt}

According to the test, the rate of CL is 1.45 while the effectiveness of UC is 0.12 and h0 rate is therefore rejected.

@@

%%R output
	Chi-squared test for given probabilities

data:  ct
X-squared = 5.4847, df = 2, p-value = 0.06442

Since our significance level is 0.05 and p > 0.05, there is no significant difference and h1 is rejected. 
%%R output

>>>>

The next step was to perform an outlier test. The method used was boxplots. As seen in Figure 3 and 4, no outliers were detected and thus no data points were removed in the tests performed.

\begin{figure}[Ht]
\centering
\includegraphics[width=90mm]{uc_box.png}
\caption{Use Case Boxplot}
\end{figure}

\begin{figure}[Ht]
\centering
\includegraphics[width=90mm]{cl_box.png}
\caption{Checklist Boxplot}
\end{figure}

\subsection{first hypothesis}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum teset was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536 H0 is rejected.

\subsection{second hyphothesis}

@@

@@

@@
